### 2020-02-28 ChapterBackground/chapterBackground.tex
Updated: Real-time Physics for Scalable Simulations in Background

\section{Scientific and Engineering Simulations}
%Real-time simulations are being used more in scientific research, however these are limited to what can be achieved on a single machine. AP allows real-time physics simulations to be scaled, enabling large or complex simulations, that otherwise wouldn’t have been able, to run in real-time.

>>>>

\section{Real-time Physics for Scalable Simulations}
%Real-time simulations are being used more in scientific research, however these are limited to what can be achieved on a single machine. AP allows real-time physics simulations to be scaled, enabling large or complex simulations, that otherwise wouldn’t have been able, to run in real-time.

In the past, real-time physics engines have not always been suitable for use in simulations \cite{Boeing2007}. However, in recent years significant effort has been put towards realism of real-time physics engines and the mathematical error has reduced. Commercial game engines (using real-time physics) are finding their use in other industries, including their application in virtual simulations (e.g. \cite{Xu2017, Lu2017, Shah2018}, collaborative VR \cite{NVIDIAHolodeck} and in film production \cite{mehta2015animated}.

%TODO: The advantages of real-time physics for non-game applications?

However, real-time physics for use in other applications has been bounded by the computational power of a single machine. For large, detailed and/or dynamic simulations, this may be insufficient \cite{koszela2018distributed}. Prior to the proprietary commercial software SpatialOS \cite{SpatialOS} and Aether Engine \cite{AetherEngine}, real-time physics simulations have been limited to what can be achieved on a single machine. Scalability in simulations can be achieved by distributing a real-time physics engine across multiple machines, alleviating the computation limit of just one machine. This would allow many more applications to take advantage of real-time physics. This study aims to bring the methods for distributing real-time physics into an academic setting for the first time.
